\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 theory.tex
theory.tex: Discussion on Fig 1

When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.  The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.  In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.

@@

{\bf TBD: add figures of $P_\kappa$ and $\xi_\pm$ for all these combinations showing that they make absolutely no difference.}

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.75\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}. \emph{Lower Panels:} Deviations with respect to the full treatment (ELS).}
 \end{center}
 \end{figure}

>>>>

When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.  The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.  In the text of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.

@@

Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.   The majority of the models agree.  The two outliers found, are the `Baseline' and `Extended' Limber cases where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.    We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.    To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.

As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.  Over angular scales used in the recent KiDS analysis (shown dashed), these curves differ by less than 1\% and such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.85\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution. \emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).    The dashed lines in the left panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
 \end{center}
 \end{figure}
